---
title: "Retrain the loyalty cohort on local data"
output: html_notebook
---
Retrain the loyalty cohort on local data using MLHO (Machine Learns Health Outcomes). This script was written by Jeff Klann, PhD and Hossein Estiri, PhD

First, run the loyalty score script AND retrain_prep.sql to set up the data for retraining. This connects to your database and loads data via the views at the end of the return rate script, retrains using R (MLHO and LASSO) based on actual return to the site. The output is a new coefficients file, which also includes the old coefficients and the optimal threshold at the Youden point for both new and old coefficients.

1) CHANGE YOUR DATABASE CONNECTION INFORMATION BELOW!
2) SET OUTPUT DIR AND SITEID BELOW!

Load the data from the database:

```{r load}
# make sure the packages are installed
if(!require(pacman)) install.packages("pacman")
pacman::p_load(data.table, devtools, backports, Hmisc, tidyr,dplyr,ggplot2,plyr,scales,readr, pROC,
               httr, DT, lubridate, latticeExtra,devtools,LiblineaR,RJDBC, scales, tidyverse,reshape2,foreach,doParallel,caret,gbm,lubridate,praznik,
               install=TRUE,update=FALSE)
if (!require(mlho)) devtools::install_github("hestiri/mlho")
options(java.parameters = "-Xmx8048m")

# This clears the global environment! Don't run this line if you need to keep your other variables around!
#rm(list=ls())

# Set an output directory and siteid - MODIFY AS NEEDED
currSiteId <- 'MGB'
out_dir <- './'


# db connection for MSSQL - MODIFY AS NEEDED
drv <- JDBC("com.microsoft.sqlserver.jdbc.SQLServerDriver",
            "/Users/jeffklann/R/sqljdbc42.jar",
            identifier.quote="`")
conn <- dbConnect(drv,
                  "jdbc:sqlserver://db.partners.org;databaseName=ACT","user","password")
# ** THIS IS FOR ORACLE
drv <- JDBC(driverClass="oracle.jdbc.OracleDriver", classPath="lib/ojdbc6.jar")
conn <- dbConnect(jdbcDriver, "jdbc:oracle:thin:@//database.hostname.com:port/service_name_or_sid", "username", "password")
# ** AN EXAMPLE OF USING ODBC instead of JDBC
#library(RODBC)
# Sys.setenv(R_MAX_NUM_DLLS = 999)
# conn <- odbcDriverConnect('driver={SQL Server};server=sv1-sqledt;database=I2B2ACT;trusted_connection=true')
# ** AN EXAMPLE OF LOADING FROM CSV FILES
# data_dir <- "~/Dropbox (Partners HealthCare)/HMS/Projects/ACT/loyalty_cohorts/mgb_returnmlho"
# dbmart <-   readr::read_csv(file.path(data_dir, "LOYALTY_MLHO_labeldt.csv"))
# dems <-   readr::read_csv(file.path(data_dir, "LOYALTY_MLHO_demographic.csv"))
# labeldt <-   readr::read_csv(file.path(data_dir, "LOYALTY_MLHO_dbmart1Y.csv"))
#coeff <- readr::read_csv("~/workspace/act_loyalty/LoyaltyCode_PSCoeff.csv")
##end of lines to modify to get your data

# Load the the basic data needed for the study.
labeldt <- dbGetQuery(conn,paste0("select * from [dbo].[LOYALTY_MLHO_LABELDT1Y_VW]"))
dems <- dbGetQuery(conn,paste0("select * from [dbo].[LOYALTY_MLHO_DEMOGRAPHIC_VW]"))
dbmart <- dbGetQuery(conn,paste0("select * from [dbo].[LOYALTY_MLHO_DBMART_VW]"))
coeff <- dbGetQuery(conn,paste0("select * from [dbo].[XREF_LOYALTYCODE_PSCOEFF]"))

# Switch column headers to lowercase
names(dems) <- tolower(names(dems))
names(dbmart) <- tolower(names(dbmart))
names(labeldt) <- tolower(names(labeldt))
names(coeff) <- tolower(names(coeff))
names(races) <- tolower(names(races))

# Save a copy of the demographics in memory because it will be truncated for MLHO
dems.save <- dems

```

Now collect a youden point and AUC for the unretrained loyalty score.

```{r originalscore}
# Correlation
cor.dat <- merge(labeldt,dems.save,by="patient_num")
uniqpats <- c(as.character(unique(dbmart$patient_num)))
cor.dat <- cor.dat %>% mutate(label_binary=(label>0))
cor.dat <- cor.dat %>% mutate(rrate = label/length(uniqpats))

# ROC curve
roc_binary <- cor.dat %>% roc("label_binary","predicted_score",ci=TRUE, ci.alpha=0.9, stratified=FALSE,
            # arguments for plot
            plot=TRUE, auc.polygon=TRUE, max.auc.polygon=TRUE, grid=TRUE,
            print.auc=TRUE, show.thres=TRUE)
youden.score <- coords(roc_binary, x="best", input="threshold", best.method="youden")
print(paste0(c("AUC and Youden point of original score:",roc_binary$auc))) 
table(youden.score)
```


MLHO modeling below:

```{r mlho}
# Set up train/test data, using a 70-30 ratio
labeldt <- subset(labeldt,labeldt$patient_num %in% dems$patient_num)
labeldt$label <- ifelse(labeldt$label >=1,1,0)
uniqpats <- c(as.character(unique(dbmart$patient_num)))
test_ind <- sample(uniqpats,
                   round(.7*length(uniqpats)))
test_labels <- subset(labeldt,labeldt$patient_num %in% c(test_ind))
print("test set lables:")
table(test_labels$label)
train_labels <- subset(labeldt,!(labeldt$patient_num %in% c(test_ind)))
print("train set lables:")
table(train_labels$label)
# train and test sets
dat.train  <- subset(dbmart,!(dbmart$patient_num %in% c(test_ind)))
dat.test <- subset(dbmart,dbmart$patient_num %in% c(test_ind))

# Format train and test data
data.table::setDT(dat.train)
dat.train[,row := .I]
dat.train$value.var <- 1
uniqpats.train <- c(as.character(unique(dat.train$patient_num)))
# MLHO requires MSMR.lite to run first for feature selection and data formatting
# We don't do feature selection here
dat.train <- MSMSR.lite(MLHO.dat=dat.train,
                        patients = uniqpats.train,
                        sparsity=0.005,
                        labels = labeldt,
                        topn=200, multicore=FALSE)
dat.test <- subset(dat.test,dat.test$phenx %in% colnames(dat.train))
setDT(dat.test)
dat.test[,row := .I]
dat.test$value.var <- 1
uniqpats.test <- c(as.character(unique(dat.test$patient_num)))
dat.test <- MSMSR.lite(MLHO.dat=dat.test,patients = uniqpats.test,sparsity=NA,jmi = FALSE,labels = labeldt, multicore=FALSE)

# Control for age and gender. Remove these columns from the select if you do not wish to.
dems <- dems %>% mutate(gender.int = ifelse(gender=='F',1,0))
dems <- dplyr::select(dems,patient_num,age,gender.int)
 
# Run LASSO
model.test <- mlearn(dat.train,
                     dat.test,
                     dems=dems,
                     save.model=TRUE,
                     classifier="regLogistic", # glm
                     note="mlho_arrival_lasso",
                     cv="cv",
                     nfold=5,
                     aoi="1y_arrival",
                     multicore=FALSE)

print(paste0("Retrained ROC"))
model.test$ROC
model.coeff <- model.test$features %>% mutate(OR=exp(coefficients))

```

```{r Save Coefficients}
# Compute the retrained score from the coefficients to get the youden threshold
newscore <- dbmart %>% inner_join(model.test$features,by=c('phenx'='features')) %>% group_by(patient_num) %>% dplyr::summarise(score=sum(coefficients))

newscore$scaledscore=rescale(newscore$score*-1) # Scaled score -- doesn't work for prediction!
newscore$score2=newscore$score*-1

scoriness <- newscore %>% inner_join(dems.save,by='patient_num') %>% select(patient_num,score2,predicted_score,scaledscore) %>% inner_join(model.test$AE, by='patient_num')

myroc <- scoriness %>% roc("actual","score2",ci=TRUE, ci.alpha=0.9, stratified=FALSE,
 # arguments for plot
 plot=TRUE, auc.polygon=TRUE, max.auc.polygon=TRUE, grid=TRUE,
 print.auc=TRUE, show.thres=TRUE)

# Compute new youden threshold
New.youden.score <- coords(myroc, x="best", input="threshold", best.method="youden")

# Compute new coeff
new.coeff <- model.test$features %>% filter(features %in% dbmart$phenx) %>% mutate(COEFF=coefficients*-1) %>% dplyr::rename(FIELD_NAME=features) %>% select(FIELD_NAME,COEFF)

# Add old coeff to table
new.coeff <- new.coeff %>% inner_join(coeff,by=c('FIELD_NAME'='field_name')) %>% dplyr::rename(ORIG_COEFF=coeff)

# Add Youden threshold to table
new.coeff <- new.coeff %>% add_row(FIELD_NAME='youden',COEFF=New.youden.score$threshold, ORIG_COEFF=youden.score$threshold) 

# Print some info 
print(paste0("Make sure this AUC is almost the same as the model AUC above, or something is amiss: ",myroc$auc))
table(New.youden.score)

# Write to disk
readr::write_csv(new.coeff,file.path(out_dir,paste0(currSiteId,'_newpscoeff.csv')))
```

```{r Save Model}
# This is an optional step - you can save the model and demographics for safekeeping if you like - it is large
results <- list(
  model.test, dems.save
)
site_results <- paste0(currSiteId, "_mlhoresults")
assign(site_results, results)
save(list = site_results, file = file.path(out_dir, paste0(currSiteId, "_mlhoreturnresults_modelonly.rda")))
```

